# Descriptive analysis of genotype data

## Setup

Set global variables and load packages and functions.

```{r setup, include=FALSE}
replicate_count = 3

require(ggplot2)
require(plyr)
require(grid)

blue = rgb(0.330, 0.484, 0.828)
light_blue = rgb(0.531, 0.639, 0.880)
dark_blue = rgb(0.198, 0.290, 0.500)
yellow = rgb(0.829, 0.680, 0.306)
light_yellow = rgb(0.880, 0.776, 0.514)
dark_yellow = rgb(0.497, 0.408, 0.183)

# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

Load marks file.

```{r load, include=FALSE}
marks_data_c = read.table("../adata/marks_data_c.tsv", header = TRUE, sep = '\t')
marks_data_x = read.table("../adata/marks_data_x.tsv", header = TRUE, sep = '\t')
```

Make function to randomly subsample to a single parasite per subject for a specific locus / mark / vaccine status combination.

```{r sample, include=FALSE}
getGtSample <- function(marks_data, input_locus, input_mark, input_status, seed=NULL) {
	marks_data <- subset(marks_data, locus == input_locus & mark_name == input_mark & vaccine_status == input_status)
	if (!is.null(seed)){ set.seed(seed) }
	marks_data <- marks_data[sample(NROW(marks_data)),]
	idx <- which(!duplicated(marks_data$subject))
	return(marks_data[idx,])
}
```

Make function to summarize mean and standard deviation of histogram bins across subsamples.

```{r summarize, include=FALSE}
average_counts_status <- function(marks_data, input_locus, input_mark, input_status) {
	tallies <- data.frame(mark_value= numeric(0), y= numeric(0), replicate = numeric(0))
	for (i in 1:replicate_count) {
		subsetted = getGtSample(marks_data, input_locus, input_mark, input_status)
		counts = ddply(subsetted, "mark_value", summarise, y = length(mark_value))
		counts$replicate <- i
		tallies <- rbind(tallies, counts)
	}
	summary = ddply(tallies,~mark_value,summarise,mean=mean(y),sd=sd(y))
	total = sum(summary$mean)
	summary$mean = summary$mean/total
	summary$sd = summary$sd/total	
	return(summary)
}

average_counts <- function(marks_data, input_locus, input_mark) {
	summary_placebo <- average_counts_status(marks_data, input_locus, input_mark, 0)
	summary_vaccine <- average_counts_status(marks_data, input_locus, input_mark, 1)
	summary_placebo$status <- 0
	summary_vaccine$status <- 1
	summary <- rbind(summary_placebo, summary_vaccine)
	return(summary)
}
```

Make plotting functions.

```{r plots, include=FALSE}
hamming_plot <- function(summary, xlabel) {
	summary$mark_value <- factor(summary$mark_value)
	summary$status <- factor(summary$status)
	ggplot(summary, aes(x=mark_value, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab(xlabel) +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +
      theme_bw()
}

match_plot <- function(summary, xlabel) {
	summary <- subset(summary, mark_value==1)
	hist <- hamming_plot(summary, xlabel) + 
	  geom_text(aes(x=mark_value, y=mean, ymax=mean, label=paste(round(mean*100,1),"%",sep="")), color="black", vjust=2.2, position = position_dodge(width=0.9)) +
	  scale_x_discrete(labels=c(""))
	return(hist)
}

match_plot <- function(summary, xlabel) {
	summary <- subset(summary, mark_value==1)
	summary$mark_value <- factor(summary$mark_value)
	summary$status <- factor(summary$status)	
	ggplot(summary, aes(x=status, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab(xlabel) +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +
	  geom_text(aes(x=status, y=mean, ymax=mean, label=paste(round(mean*100,1),"%",sep="")), color="black", vjust=2.2, position = position_dodge(width=0.9)) +
	  scale_x_discrete(labels=c("")) +
      theme_bw()
}
```

## Clinical

### Match vs mismatch

```{r match-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE}
pTEP = match_plot(average_counts(marks_data_c, "TEP", "match_3D7"), "Match TEP")
pUnnamed = match_plot(average_counts(marks_data_c, "Unnamed", "match_3D7"), "Match Unnamed")
pTh2R = match_plot(average_counts(marks_data_c, "Th2R", "match_3D7"), "Match Th2R")
pTh3R = match_plot(average_counts(marks_data_c, "Th3R", "match_3D7"), "Match Th3R")
pSERA2 = match_plot(average_counts(marks_data_c, "SERA2", "match_3D7"), "Match SERA2")
pTRAP = match_plot(average_counts(marks_data_c, "TRAP", "match_3D7"), "Match TRAP")
multiplot(pTEP, pUnnamed, pTh2R, pTh3R, pSERA2, pTRAP, cols=2, layout=matrix(c(1,2,3,4,5,6), nrow=3, byrow=TRUE))
```

### Hamming distance

```{r hamming-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE}
pTEP = hamming_plot(average_counts(marks_data_c, "TEP", "hamming_3D7"), "Hamming distance TEP")
pUnnamed = hamming_plot(average_counts(marks_data_c, "Unnamed", "hamming_3D7"), "Hamming distance Unnamed")
pTh2R = hamming_plot(average_counts(marks_data_c, "Th2R", "hamming_3D7"), "Hamming distance Th2R")
pTh3R = hamming_plot(average_counts(marks_data_c, "Th3R", "hamming_3D7"), "Hamming distance Th3R")
pSERA2 = hamming_plot(average_counts(marks_data_c, "SERA2", "hamming_3D7"), "Hamming distance SERA2")
pTRAP = hamming_plot(average_counts(marks_data_c, "TRAP", "hamming_3D7"), "Hamming distance TRAP")
multiplot(pTEP, pUnnamed, pTh2R, pTh3R, pSERA2, pTRAP, cols=2, layout=matrix(c(1,2,3,4,5,6), nrow=3, byrow=TRUE))
```

## Cross-sectional

### Match vs mismatch

```{r match-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE}
pTEP = match_plot(average_counts(marks_data_x, "TEP", "match_3D7"), "Match TEP")
pUnnamed = match_plot(average_counts(marks_data_x, "Unnamed", "match_3D7"), "Match Unnamed")
pTh2R = match_plot(average_counts(marks_data_x, "Th2R", "match_3D7"), "Match Th2R")
pTh3R = match_plot(average_counts(marks_data_x, "Th3R", "match_3D7"), "Match Th3R")
pSERA2 = match_plot(average_counts(marks_data_x, "SERA2", "match_3D7"), "Match SERA2")
pTRAP = match_plot(average_counts(marks_data_x, "TRAP", "match_3D7"), "Match TRAP")
multiplot(pTEP, pUnnamed, pTh2R, pTh3R, pSERA2, pTRAP, cols=2, layout=matrix(c(1,2,3,4,5,6), nrow=3, byrow=TRUE))
```

### Hamming distance

```{r hamming-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE}
pTEP = hamming_plot(average_counts(marks_data_x, "TEP", "hamming_3D7"), "Hamming distance TEP")
pUnnamed = hamming_plot(average_counts(marks_data_x, "Unnamed", "hamming_3D7"), "Hamming distance Unnamed")
pTh2R = hamming_plot(average_counts(marks_data_x, "Th2R", "hamming_3D7"), "Hamming distance Th2R")
pTh3R = hamming_plot(average_counts(marks_data_x, "Th3R", "hamming_3D7"), "Hamming distance Th3R")
pSERA2 = hamming_plot(average_counts(marks_data_x, "SERA2", "hamming_3D7"), "Hamming distance SERA2")
pTRAP = hamming_plot(average_counts(marks_data_x, "TRAP", "hamming_3D7"), "Hamming distance TRAP")
multiplot(pTEP, pUnnamed, pTh2R, pTh3R, pSERA2, pTRAP, cols=2, layout=matrix(c(1,2,3,4,5,6), nrow=3, byrow=TRUE))
```
