# Descriptive analysis of genotype data

## Setup

Set global variables and load packages and functions.

```{r setup, include=FALSE}
replicate_count = 50

require(ggplot2)
require(plyr)
require(grid)

blue = rgb(0.330, 0.484, 0.828)
light_blue = rgb(0.531, 0.639, 0.880)
dark_blue = rgb(0.198, 0.290, 0.500)
yellow = rgb(0.829, 0.680, 0.306)
light_yellow = rgb(0.880, 0.776, 0.514)
dark_yellow = rgb(0.497, 0.408, 0.183)
```

Load marks file.

```{r load, include=FALSE}
marks_data_c = read.table("../adata/marks_data_c.tsv", header = TRUE, sep = '\t', na.strings = "NULL")
marks_data_x = read.table("../adata/marks_data_x.tsv", header = TRUE, sep = '\t', na.strings = "NULL")
```

Subset to just the 5 major sites.

```{r initial_subset, include=FALSE}
marks_data_c <- subset(marks_data_c, study_site == "Agogo" || study_site == "Kintampo" || study_site == "Kombewa" || study_site == "Nanoro" || study_site == "Siaya")
marks_data_x <- subset(marks_data_x, study_site == "Agogo" || study_site == "Kintampo" || study_site == "Kombewa" || study_site == "Nanoro" || study_site == "Siaya")
```

Make function to randomly subsample to a single parasite per subject for a specific locus / mark / vaccine status combination.

```{r sample, include=FALSE}
getGtSample <- function(marks_data, input_locus, input_mark, input_age, input_status, input_site=NULL, seed=NULL) {
	marks_data <- subset(marks_data, locus == input_locus & mark_name == input_mark & age_cohort == input_age & vaccine_status == input_status)	
	if (!is.null(input_site)) {
		marks_data <- subset(marks_data, study_site == input_site)
	}
	if (!is.null(seed)){ set.seed(seed) }
	marks_data <- marks_data[sample(NROW(marks_data)),]
	idx <- which(!duplicated(marks_data$subject))
	return(marks_data[idx,])
}
```

Make function to summarize mean and standard deviation of histogram bins across subsamples.

```{r summarize, include=FALSE}
average_counts_status <- function(marks_data, input_locus, input_mark, input_age, input_status, input_site=NULL) {
	tallies <- data.frame(mark_value= numeric(0), y= numeric(0), replicate = numeric(0))
	for (i in 1:replicate_count) {
		subsetted = getGtSample(marks_data, input_locus, input_mark, input_age, input_status, input_site)
		subsetted = subset(subsetted, mark_value >= 0)
		counts = ddply(subsetted, "mark_value", summarise, y = length(mark_value))
		counts$replicate <- i
		tallies <- rbind(tallies, counts)
	}
	summary = ddply(tallies,~mark_value,summarise,mean=mean(y),sd=sd(y))
	total = sum(summary$mean)
	summary$mean = summary$mean/total
	summary$sd = summary$sd/total	
	return(summary)
}

average_counts_locus <- function(marks_data, input_locus, input_mark, input_age, input_site=NULL) {
	summary_placebo <- average_counts_status(marks_data, input_locus, input_mark, input_age, 0, input_site)
	summary_vaccine <- average_counts_status(marks_data, input_locus, input_mark, input_age, 1, input_site)
	summary_placebo$status <- 0
	summary_vaccine$status <- 1
	summary <- rbind(summary_placebo, summary_vaccine)
	return(summary)
}

average_counts <- function(marks_data, input_mark, input_age, input_site=NULL) {
	summary_TEP <- average_counts_locus(marks_data, "TEP", input_mark, input_age, input_site)
	summary_Th2R <- average_counts_locus(marks_data, "Th2R", input_mark, input_age, input_site)
	summary_Th3R <- average_counts_locus(marks_data, "Th3R", input_mark, input_age, input_site)
	summary_LD <- average_counts_locus(marks_data, "LD", input_mark, input_age, input_site)	
	summary_Unnamed <- average_counts_locus(marks_data, "Unnamed", input_mark, input_age, input_site)	
	summary_SERA2 <- average_counts_locus(marks_data, "SERA2", input_mark, input_age, input_site)
	summary_TEP$locus <- "TEP"
	summary_Th2R$locus <- "Th2R"	
	summary_Th3R$locus <- "Th3R"
	summary_LD$locus <- "LD"	
	summary_Unnamed$locus <- "Unnamed"			
	summary_SERA2$locus <- "SERA2"				
	summary <- rbind(summary_TEP, summary_Th2R, summary_Th3R, summary_LD, summary_Unnamed, summary_SERA2)	
	return(summary)
}

average_counts_across_sites <- function(marks_data, input_locus, input_mark, input_age) {
	summary_Agogo <- average_counts_locus(marks_data, input_locus, input_mark, input_age, "Agogo")
	summary_Kintampo <- average_counts_locus(marks_data, input_locus, input_mark, input_age, "Kintampo")
	summary_Kombewa <- average_counts_locus(marks_data, input_locus, input_mark, input_age, "Kombewa")
	summary_Nanoro <- average_counts_locus(marks_data, input_locus, input_mark, input_age, "Nanoro")
	summary_Siaya <- average_counts_locus(marks_data, input_locus, input_mark, input_age, "Siaya")
	summary_Agogo$study_site <- "Agogo"
	summary_Kintampo$study_site <- "Kintampo"	
	summary_Kombewa$study_site <- "Kombewa"	
	summary_Nanoro$study_site <- "Nanoro"	
	summary_Siaya$study_site <- "Siaya"				
	summary <- rbind(summary_Agogo, summary_Kintampo, summary_Kombewa, summary_Nanoro, summary_Siaya)	
	summary$locus <- input_locus		
	return(summary)
}				
```

Make plotting functions.

```{r plots, include=FALSE}
moi_plot <- function(summary, endpointLabel, cohortLabel, siteLabel) {
	summary$mark_value <- factor(summary$mark_value)
	summary$status <- factor(summary$status)
	title = paste("Multiplicity of infection\nEndpoint:", endpointLabel, "\nAge Cohort:", cohortLabel, "\nSite:", siteLabel)	
	p <- ggplot(summary, aes(x=mark_value, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("MOI") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +   
      theme_bw() +
      ggtitle(title)   	      
	return(p)
}

match_plot <- function(summary, endpointLabel, cohortLabel, siteLabel) {
	summary <- subset(summary, mark_value==1)
	summary$mark_value <- factor(summary$mark_value)
	summary$locus <- factor(summary$locus, levels = c("TEP", "Th2R", "Th3R", "LD", "Unnamed", "SERA2"))	
	summary$status <- factor(summary$status)
	title = paste("Match to 3D7 across genomic regions\nEndpoint:", endpointLabel, "\nAge Cohort:", cohortLabel, "\nSite:", siteLabel)
	p <- ggplot(summary, aes(x=status, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Match") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +
	  geom_text(aes(x=status, y=mean, ymax=mean, label=paste(round(mean*100,1),"%",sep="")), color="black", vjust=2.2, position = position_dodge(width=0.9)) +
	  scale_x_discrete(labels=c(""), drop=FALSE) +
	  facet_wrap(~ locus, scales="free") +
	  theme_bw() +
      ggtitle(title)   	  	  
	return(p)
}

match_plot_sites <- function(summary, endpointLabel, locusLabel, cohortLabel) {
	summary <- subset(summary, mark_value==1)
	summary$mark_value <- factor(summary$mark_value)
	summary$locus <- factor(summary$locus, levels = c("TEP", "Th2R", "Th3R", "LD", "Unnamed", "SERA2"))	
	summary$study_site <- factor(summary$study_site, levels = c("Agogo", "Kintampo", "Kombewa", "Nanoro", "Siaya"))		
	summary$status <- factor(summary$status)	
	title = paste("Match to 3D7 across study sites\nEndpoint:", endpointLabel, "\nGenomic region:", locusLabel, "\nAge Cohort:", cohortLabel)	
	p <- ggplot(summary, aes(x=status, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Match") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +
	  geom_text(aes(x=status, y=mean, ymax=mean, label=paste(round(mean*100,1),"%",sep="")), color="black", vjust=2.2, position = position_dodge(width=0.9)) +
	  scale_x_discrete(labels=c(""), drop=FALSE) +
	  facet_wrap(~ study_site, scales="free") + 
	  theme_bw() +
      ggtitle(title)   	  
	return(p)
}

hamming_plot <- function(summary, endpointLabel, cohortLabel, siteLabel) {
	summary$mark_value <- factor(summary$mark_value)
	summary$locus <- factor(summary$locus, levels = c("TEP", "Th2R", "Th3R", "LD", "Unnamed", "SERA2"))	
	summary$status <- factor(summary$status)
	title = paste("Hamming distance to 3D7 across genomic regions\nEndpoint:", endpointLabel, "\nAge Cohort:", cohortLabel, "\nSite:", siteLabel)	
	p <- ggplot(summary, aes(x=mark_value, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Hamming distance") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) + 
	  facet_wrap(~ locus, scales="free") + 	  
      theme_bw() +
      ggtitle(title)   	      
	return(p)
}

hamming_plot_sites <- function(summary, endpointLabel, locusLabel, cohortLabel) {
	summary$mark_value <- factor(summary$mark_value)
	summary$locus <- factor(summary$locus, levels = c("TEP", "Th2R", "Th3R", "LD", "Unnamed", "SERA2"))	
	summary$study_site <- factor(summary$study_site, levels = c("Agogo", "Kintampo", "Kombewa", "Nanoro", "Siaya"))			
	summary$status <- factor(summary$status)
	title = paste("Hamming distances to 3D7 across study sites\nEndpoint:", endpointLabel, "\nGenomic region:", locusLabel, "\nAge Cohort:", cohortLabel)
	p <- ggplot(summary, aes(x=mark_value, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Hamming distance") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +  
	  facet_wrap(~ study_site, scales="free") + 	  
      theme_bw() +
      ggtitle(title)   
	return(p)
}

bep_match_plot <- function(summary, endpointLabel, cohortLabel, siteLabel) {
	summary <- subset(summary, mark_value==1)
	summary$mark_value <- factor(summary$mark_value)
	summary$status <- factor(summary$status)
	title = paste("Match to 3D7 in BEP repeat count\nEndpoint:", endpointLabel, "\nAge Cohort:", cohortLabel, "\nSite:", siteLabel)
	p <- ggplot(summary, aes(x=status, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Match") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +
	  geom_text(aes(x=status, y=mean, ymax=mean, label=paste(round(mean*100,1),"%",sep="")), color="black", vjust=2.2, position = position_dodge(width=0.9)) +
	  scale_x_discrete(labels=c(""), drop=FALSE) +
	  theme_bw() +
      ggtitle(title)   	  	  
	return(p)
}

bep_hist_plot <- function(summary, endpointLabel, cohortLabel, siteLabel) {
	summary$mark_value <- factor(summary$mark_value)
	summary$status <- factor(summary$status)
	title = paste("Histogram of BEP repeat count\nEndpoint:", endpointLabel, "\nAge Cohort:", cohortLabel, "\nSite:", siteLabel)	
	p <- ggplot(summary, aes(x=mark_value, y=mean, fill=status, color=status)) +
      geom_bar(position=position_dodge(), stat="identity") +
	  geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2, position=position_dodge(.9)) +      
      xlab("Hamming distance") +
      ylab("Proportion") +
	  scale_fill_manual(values=c(light_blue, light_yellow), labels=c("Placebo", "Vaccine")) +
	  scale_color_manual(values=c(dark_blue, dark_yellow), guide=FALSE) +   
      theme_bw() +
      ggtitle(title)   	      
	return(p)
}
```

## Descriptive plots

```{r moi-newborn-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of multiplicity'}
endpoint = "Clinical Malaria by Month 14"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "NA", "multiplicity", age)
moi_plot(summary, endpoint, age, site)
```

```{r moi-infant-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of multiplicity'}
endpoint = "Clinical Malaria by Month 14"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "NA", "multiplicity", age)
moi_plot(summary, endpoint, age, site)
```

```{r match-newborn-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts(marks_data_c, "match_3D7", age)
match_plot(summary, endpoint, age, site)
```

```{r hamming-newborn-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts(marks_data_c, "hamming_3D7", age)
hamming_plot(summary, endpoint, age, site)
```

```{r match-infant-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts(marks_data_c, "match_3D7", age)
match_plot(summary, endpoint, age, site)
```

```{r hamming-infant-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts(marks_data_c, "hamming_3D7", age)
hamming_plot(summary, endpoint, age, site)
```

```{r match-newborn-sites-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
locus = "TEP"
age = "6-12 weeks"
summary = average_counts_across_sites(marks_data_c, locus, "match_3D7", age)
match_plot_sites(summary, endpoint, locus, age)
```

```{r hamming-newborn-sites-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
locus = "TEP"
age = "6-12 weeks"
summary = average_counts_across_sites(marks_data_c, locus, "hamming_3D7", age)
hamming_plot_sites(summary, endpoint, locus, age)
```

```{r match-infant-sites-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
locus = "TEP"
age = "5-17 months"
summary = average_counts_across_sites(marks_data_c, locus, "match_3D7", age)
match_plot_sites(summary, endpoint, locus, age)
```

```{r hamming-infant-sites-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Clinical Malaria by Month 14"
locus = "TEP"
age = "5-17 months"
summary = average_counts_across_sites(marks_data_c, locus, "hamming_3D7", age)
hamming_plot_sites(summary, endpoint, locus, age)
```

```{r bep-match-newborn-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in NANP repeat region'}
endpoint = "Clinical Malaria by Month 14"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "match_3D7", age)
bep_match_plot(summary, endpoint, age, site)
```

```{r bep-match-infact-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in NANP repeat region'}
endpoint = "Clinical Malaria by Month 14"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "match_3D7", age)
bep_match_plot(summary, endpoint, age, site)
```

```{r bep-hist-newborn-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of NANP repeat distribution'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "repeat_count", age)
bep_hist_plot(summary, endpoint, age, site)
```

```{r bep-hist-infant-c, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of NANP repeat distribution'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "repeat_count", age)
bep_hist_plot(summary, endpoint, age, site)
```

```{r moi-newborn-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of multiplicity'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_x, "NA", "multiplicity", age)
moi_plot(summary, endpoint, age, site)
```

```{r moi-infant-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of multiplicity'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_x, "NA", "multiplicity", age)
moi_plot(summary, endpoint, age, site)
```

```{r match-newborn-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts(marks_data_x, "match_3D7", age)
match_plot(summary, endpoint, age, site)
```

```{r hamming-newborn-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts(marks_data_x, "hamming_3D7", age)
hamming_plot(summary, endpoint, age, site)
```

```{r match-infant-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts(marks_data_x, "match_3D7", age)
match_plot(summary, endpoint, age, site)
```

```{r hamming-infant-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts(marks_data_x, "hamming_3D7", age)
hamming_plot(summary, endpoint, age, site)
```

```{r match-newborn-sites-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
locus = "TEP"
age = "6-12 weeks"
summary = average_counts_across_sites(marks_data_x, locus, "match_3D7", age)
match_plot_sites(summary, endpoint, locus, age)
```

```{r hamming-newborn-sites-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
locus = "TEP"
age = "6-12 weeks"
summary = average_counts_across_sites(marks_data_x, locus, "hamming_3D7", age)
hamming_plot_sites(summary, endpoint, locus, age)
```

```{r match-infant-sites-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
locus = "TEP"
age = "5-17 months"
summary = average_counts_across_sites(marks_data_x, locus, "match_3D7", age)
match_plot_sites(summary, endpoint, locus, age)
```

```{r hamming-infant-sites-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of Hamming distance to 3D7 in C-terminus CSP'}
endpoint = "Any Malaria by Month 20"
locus = "TEP"
age = "5-17 months"
summary = average_counts_across_sites(marks_data_x, locus, "hamming_3D7", age)
hamming_plot_sites(summary, endpoint, locus, age)
```

```{r bep-match-newborn-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in NANP repeat region'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "match_3D7", age)
bep_match_plot(summary, endpoint, age, site)
```

```{r bep-match-infact-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of match to 3D7 in NANP repeat region'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_c, "BEP", "match_3D7", age)
bep_match_plot(summary, endpoint, age, site)
```

```{r bep-hist-newborn-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of NANP repeat distribution'}
endpoint = "Any Malaria by Month 20"
age = "6-12 weeks"
site = "5 major pooled"
summary = average_counts_locus(marks_data_x, "BEP", "repeat_count", age)
bep_hist_plot(summary, endpoint, age, site)
```

```{r bep-hist-infant-x, dpi=150, fig.path='figures/', echo=FALSE, warning=FALSE, message=FALSE, dev=c('png', 'pdf'), fig.cap='Descriptive plot of NANP repeat distribution'}
endpoint = "Any Malaria by Month 20"
age = "5-17 months"
site = "5 major pooled"
summary = average_counts_locus(marks_data_x, "BEP", "repeat_count", age)
bep_hist_plot(summary, endpoint, age, site)
```